---
title: "Thesis Study 1"
output: html_document
date: "2024-01-10"
---


```{r setup, include=FALSE}



library(tidyverse)
library (dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(lmerTest)
library(viridis)
library(hrbrthemes)
library(fmsb)
library(colormap)


data <- read.csv("Study 1 data for r.csv")

```

#AMQ Variables


```{r desriptive stats- amq-see}

hist(data$AMQ_see)

mean(data$AMQ_see)
sd(data$AMQ_see)


```



```{r amq-see}



model_see <- glmer(AMQ_see ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition + (1|Participant), data=data, family="gaussian")
summary(model_see)


figure_see <- ggplot(data, aes(x=memory_type, y=AMQ_see)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_see

```


Memory condition and rehearsal are significant.
Interaction is aso significant.


```{r ttest amq}

data_ttest_1 <- data %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_ttest_2 <- data %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_ttest <- bind_rows(data_ttest_1, data_ttest_2)  
data_ttest$condition <- paste(data_ttest$memory_type, data_ttest$rehearsed_condition, sep="_")

ttest_see <- t.test(AMQ_see ~ condition, data=data_ttest)
ttest_see
```
Independent sample t-test is not significant different


```{r desriptive stats- amq-hear}

hist(data$AMQ_hear)

mean(data$AMQ_hear)
sd(data$AMQ_hear)


```


```{r amq-hear}

model_see <- lm(AMQ_hear ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_see)

figure_hear <- ggplot(data, aes(x=memory_type, y=AMQ_hear)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_hear

```

significant effect of rehearsed condition
no sigfnicant effect of memory type 
no interaction



```{r ttest amq-hear}

data_ttest_2 <- data %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_ttest_2 <- data %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_ttest <- bind_rows(data_ttest_1, data_ttest_2)  
data_ttest$condition <- paste(data_ttest$memory_type, data_ttest$rehearsed_condition, sep="_")

ttest_hear <- t.test(AMQ_hear ~ condition, data=data_ttest)
ttest_hear
```
significant t-test! Higher for fictional memories than personal non-reherased memories.

```{r desriptive stats- amq-accuary}

hist(data$AMQ_Accuracy)

mean(data$AMQ_Accuracy)
sd(data$AMQ_Accuracy)


```

```{r amq-accuracy}

model_see <- lm(AMQ_Accuracy ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_see)

figure_see <- ggplot(data, aes(x=memory_type, y= AMQ_Accuracy)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_see





```



```{r ttest amq-}



ttest_acc <- t.test(AMQ_Accuracy ~ condition, data=data_ttest)
ttest_acc
```

no significant differece found in t-test



```{r amq-live}

model_live <- lm(AMQ_Live ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_live)

figure_live <- ggplot(data, aes(x=memory_type, y= AMQ_Live)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_live





```
No interaction
significant differebce between memory type and rehersal

```{r ttest amq-live}



ttest_live <- t.test(AMQ_Live ~ condition, data=data_ttest)
ttest_live
```
Not a significant t-test (mean for personal is higher)



```{r amq-strength}

model_str <- lm(AMQ_Strength ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_str)

figure_str <- ggplot(data, aes(x=memory_type, y= AMQ_Strength)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_str





```

no interaction
main effect of rehearsed condition



```{r ttest amq-str}



ttest_str <- t.test(AMQ_Strength ~ condition, data=data_ttest)
ttest_str
```

Significant difference!
Strength of emotions was stronger for rehearsed fictional memories than non-rehearsed personal memories



```{r amq-positivity}

model_pos <- lm(AMQ_Positivity ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_pos)

figure_pos <- ggplot(data, aes(x=memory_type, y= AMQ_Positivity)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_pos





```

nothing significant :0
but we can see that rehersal 0 has lower positivity levels than rehersa 1 memories



```{r ttest amq-positivity}



ttest_pos <- t.test(AMQ_Positivity ~ condition, data=data_ttest)
ttest_pos
```


no sig diffenrece

fiction 1 > personal 0 




```{r amq-negativity}

model_neg <- lm(AMQ_Negativity ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_neg)

figure_neg <- ggplot(data, aes(x=memory_type, y= AMQ_Negativity)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_neg





```

no sig difference either (different from what we saw in brenda's study 2...)




```{r ttest amq-positivity}



ttest_neg <- t.test(AMQ_Negativity ~ condition, data=data_ttest)
ttest_neg
```
^^ almost the same



```{r amq-intensity}

model_intense <- lm(AMQ_Intensity ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_intense)

figure_intense <- ggplot(data, aes(x=memory_type, y= AMQ_Intensity)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_intense





```


significant effect of condition!
no interaction




```{r ttest amq-intensity}



ttest_int <- t.test(AMQ_Intensity ~ condition, data=data_ttest)
ttest_int
```
Significant difference according to t-test



```{r tale-1}

model_tale1 <- lm(TALE_1 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale1)

figure_tale1 <- ggplot(data, aes(x=memory_type, y= TALE_1)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_tale1





```

no main effects
no interaction






```{r ttest TALE1}



ttest_TALE_1 <- t.test(TALE_1 ~ condition, data=data_ttest)
ttest_TALE_1
```
No sig difference
averages are virtually the same



```{r tale-2}

model_tale2 <- lm(TALE_2 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale2)

figure_tale2 <- ggplot(data, aes(x=memory_type, y= TALE_2)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_tale2





```
no main effects
no interaction




```{r ttest TALE2}



ttest_TALE_2 <- t.test(TALE_2 ~ condition, data=data_ttest)
ttest_TALE_2
```
no sig diff (averages are virtually the same)





```{r tale-4}




#for these memories we are not getting a normal distribution whatsover. data is heavily skewed

hist(data$TALE_4)

mean(data$TALE_4)
sd(data$TALE_4)



model_tale4 <- lm(TALE_4 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale4)

figure_TALE4 <- ggplot(data, aes(x=memory_type, y= TALE_4)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_TALE4





```







```{r ttest TALE4}



ttest_TALE_4 <- t.test(TALE_4 ~ condition, data=data_ttest)
ttest_TALE_4
```
no sig diff (well duh!)




```{r tale-5}



#for these memories we are not getting a normal distribution whatsover. data is heavily skewed

hist(data$TALE_5)

mean(data$TALE_5)
sd(data$TALE_5)



model_tale5 <- lm(TALE_5 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale5)

figure_TALE5 <- ggplot(data, aes(x=memory_type, y= TALE_5)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_TALE5





```




```{r ttest TALE5}



ttest_TALE_5 <- t.test(TALE_5 ~ condition, data=data_ttest)
ttest_TALE_5
```




```{r tale-6}



#for these memories we are not getting a normal distribution whatsover. data is heavily skewed

hist(data$TALE_6)

mean(data$TALE_6)
sd(data$TALE_6)


model_tale6 <- lm(TALE_6 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale6)

figure_TALE6 <- ggplot(data, aes(x=memory_type, y= TALE_6)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_TALE6



```
no interaction nor main effects





```{r ttest TALE5}



ttest_TALE_6 <- t.test(TALE_6 ~ condition, data=data_ttest)
ttest_TALE_6
```
no sig difference (bruh)




```{r CES1}

model_CES1 <- lm(CES_1 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_CES1)

figure_CES1 <- ggplot(data, aes(x=memory_type, y= CES_1)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_CES1



```
small effect of rehearsed



```{r ttest ces1}



ttest_CES1 <- t.test(CES_1 ~ condition, data=data_ttest)
ttest_CES1
```
no significant difference



```{r CES2}

model_CES2 <- lm(CES_2 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_CES2)

figure_CES2 <- ggplot(data, aes(x=memory_type, y= CES_2)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_CES2



```

no significant predictors




```{r ttest ces2}



ttest_CES2 <- t.test(CES_2 ~ condition, data=data_ttest)
ttest_CES2
```
no significant difference between two means


```{r CES3}

model_CES3 <- lm(CES_3 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_CES3)

figure_CES3 <- ggplot(data, aes(x=memory_type, y= CES_3)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_CES3



data %>%
filter(memory_type == "personal" & rehearsed_condition == 1) %>%
summarize(mean(CES_3))




data %>%
filter(memory_type == "personal" & rehearsed_condition == 0) %>%
summarize(mean(CES_3))





data %>%
filter(memory_type == "fiction" & rehearsed_condition == 1) %>%
summarize(mean(CES_3))




data %>%
filter(memory_type == "fiction" & rehearsed_condition == 0) %>%
summarize(mean(CES_3))



#is there an easier way to get this frequency table?



```
there is an interaction!
(not sure what it means though lol)




```{r ttest ces3}



ttest_CES3 <- t.test(CES_3 ~ condition, data=data_ttest)
ttest_CES3
```
same means! (no significance at all!)


```{r CES4}

model_CES4 <- lm(CES_4 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_CES4)

figure_CES4 <- ggplot(data, aes(x=memory_type, y= CES_4)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_CES4



```
significant effect of rehearsed!
no main effect of memory type
no interaction

# tale functions but with directive, social and self


```{r tale-directive}


tale_directive <- data %>% 
  mutate(directive_TALE= (TALE_1 + TALE_6)/2)

model_directive <- lm(directive_TALE ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=tale_directive)
summary(model_directive)

figure_tale_directive <- ggplot(tale_directive, aes(x=memory_type, y= directive_TALE)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_tale_directive





```
nothing significant
- no main effects nor interactions






```{r ttest tale directive}






data_directive_1 <- tale_directive %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_directive_2 <- tale_directive %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_directive <- bind_rows(data_directive_1, data_directive_2)  
data_directive$condition <- paste(data_directive$memory_type, data_directive$rehearsed_condition, sep="_")

ttest_directive <- t.test( directive_TALE ~ condition, data=data_directive)
ttest_directive


```



```{r tale-self}


tale_self <- data %>% 
  mutate(self_TALE= (TALE_2 + TALE_4)/2)

model_self <- lm(self_TALE ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=tale_self)
summary(model_self)

figure_tale_self <- ggplot(tale_self, aes(x=memory_type, y= self_TALE)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_tale_self





```
no main effects and no interaction



```{r ttest tale self}






data_self_1 <- tale_self %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_self_2 <- tale_self %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_self <- bind_rows(data_self_1, data_self_2)  
data_self$condition <- paste(data_self$memory_type, data_self$rehearsed_condition, sep="_")

ttest_self <- t.test(self_TALE ~ condition, data=data_self)
ttest_self


```



# social tale function



```{r tale-5}



#for these memories we are not getting a normal distribution whatsover. data is heavily skewed

hist(data$TALE_5)

mean(data$TALE_5)
sd(data$TALE_5)



model_tale5 <- lm(TALE_5 ~ rehearsed_condition + memory_type + memory_type:rehearsed_condition, data=data)
summary(model_tale5)

figure_TALE5 <- ggplot(data, aes(x=memory_type, y= TALE_5)) +
  facet_grid(~as.factor(rehearsed_condition)) +
  geom_boxplot()

figure_TALE5





```
no main effects or interaction!


```{r ttest TALE5}



ttest_TALE_5 <- t.test(TALE_5 ~ condition, data=data_ttest)
ttest_TALE_5

```
no significant difference between the two groups



```{r create spider plot}

  # https://www.data-to-viz.com/caveat/spider.html



# Create data
set.seed(1)
data <-as.data.frame(matrix( c( sample( 2: 6 , 9 , replace=T), sample( 2:6 , 9 , replace=T)) , ncol=9, byrow=TRUE))
colnames(data) <- c("rehersal" , "see" , "hear" , "accuracy" , "live", "strength" , "positivity" , "negativity", "intensity" )


data <-rbind(rep(6,9) , rep(0,9) , data)



data <-rbind(rep(20,10) , rep(0,10) , data)

# Prepare color
colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9)  )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4)  )

# Custom the radarChart !
radarchart( data, axistype=1, 

  #custom polygon
  pcol=colors_border , pfcol=colors_in , plwd=4, plty=1 , 

  #custom the grid
  cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=1.1,

  #custom labels
  vlcex=0.8 
  )
# Legend
legend(x=0.85, y=1, legend = c("Shirley", "Sonia"), bty = "n", pch=20 , col=colors_border , text.col = "black", cex=0.9, pt.cex=1.6)


```

```{r means-sds}


means_data <- data %>% 
  summarize(mean_AMQsee= mean(AMQ_see), se_AMQsee= (sd(AMQ_see)/ (n() -1)), 
          mean_AMQhear= mean(AMQ_hear), se_AMQhear= (sd(AMQ_hear)/ (n() -1) ),
          mean_AMQlive= mean(AMQ_Live), se_AMQlive= (sd(AMQ_Live)/ (n() -1) ),
          mean_AMQstrength= mean(AMQ_Strength), se_AMQstrength= (sd(AMQ_Strength)/ (n() -1) ),
          mean_AMQpositivity= mean(AMQ_Positivity), se_AMQpositivity= (sd(AMQ_Positivity)/ (n() -1) ),
          mean_AMQnegativity= mean(AMQ_Negativity), se_AMQnegativity= (sd(AMQ_Negativity)/ (n() -1) ),
          mean_AMQaccuracy= mean(AMQ_Accuracy), se_AMQaccuracy= (sd(AMQ_Accuracy)/ (n() -1) ),
          mean_AMQrehersal= mean(AMQ_Rehersal), se_AMQrehersal= (sd(AMQ_Rehersal)/ (n() -1) ),
          mean_AMQintensity= mean(AMQ_Intensity),se_AMQintensity = (sd(AMQ_Intensity)/ (n() -1)))



means_data_long <- pivot_longer(means_data, everything(), names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide <- pivot_wider(means_data_long, names_from = measure, values_from = value)


library(ggthemes)

ggplot(means_data_wide, aes(x=mean, y= variable)) +
  geom_point(size= 3.5, color= 'lightblue') +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se), color="lightblue", width= 0.5, size= 1) +
  #coord_cartesian(xlim=c(1,7)) +
  theme_classic()
  
  



```



```{r means-sds-condition}


means_data <- data %>% 
group_by(memory_type) %>% 

  summarize(mean_AMQsee= mean(AMQ_see), se_AMQsee= (sd(AMQ_see)/ (n() -1)), 
          mean_AMQhear= mean(AMQ_hear), se_AMQhear= (sd(AMQ_hear)/ (n() -1) ),
             mean_AMQlive= mean(AMQ_Live), se_AMQlive= (sd(AMQ_Live)/ (n() -1) ),
          mean_AMQstrength= mean(AMQ_Strength), se_AMQstrength= (sd(AMQ_Strength)/ (n() -1) ),
          mean_AMQpositivity= mean(AMQ_Positivity), se_AMQpositivity= (sd(AMQ_Positivity)/ (n() -1) ),
          mean_AMQnegativity= mean(AMQ_Negativity), se_AMQnegativity= (sd(AMQ_Negativity)/ (n() -1) ),
          mean_AMQaccuracy= mean(AMQ_Accuracy), se_AMQaccuracy= (sd(AMQ_Accuracy)/ (n() -1) ),
          mean_AMQrehersal= mean(AMQ_Rehersal), se_AMQrehersal= (sd(AMQ_Rehersal)/ (n() -1) ),
          mean_AMQintensity= mean(AMQ_Intensity),se_AMQintensity = (sd(AMQ_Intensity)/ (n() -1)))



means_data_long <- pivot_longer(means_data, -memory_type, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide <- pivot_wider(means_data_long, names_from = measure, values_from = value)


library(ggthemes)

ggplot(means_data_wide, aes(x=mean, y= variable, color= memory_type)) +
  geom_point(size= 3.5) +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se),  width= 0.5, size= 1) +
  coord_cartesian(xlim=c(1,7)) +
  theme_classic()





```
```{r facet-grid-graph}


means_data_rehearsed <- data %>% 
  filter(rehearsed_condition== 1)  %>% 
group_by(memory_type) %>% 

  summarize(mean_AMQsee= mean(AMQ_see), se_AMQsee= (sd(AMQ_see)/ (n() -1)), 
          mean_AMQhear= mean(AMQ_hear), se_AMQhear= (sd(AMQ_hear)/ (n() -1) ),
             mean_AMQlive= mean(AMQ_Live), se_AMQlive= (sd(AMQ_Live)/ (n() -1) ),
          mean_AMQstrength= mean(AMQ_Strength), se_AMQstrength= (sd(AMQ_Strength)/ (n() -1) ),
          mean_AMQpositivity= mean(AMQ_Positivity), se_AMQpositivity= (sd(AMQ_Positivity)/ (n() -1) ),
          mean_AMQnegativity= mean(AMQ_Negativity), se_AMQnegativity= (sd(AMQ_Negativity)/ (n() -1) ),
          mean_AMQaccuracy= mean(AMQ_Accuracy), se_AMQaccuracy= (sd(AMQ_Accuracy)/ (n() -1) ),
          mean_AMQrehersal= mean(AMQ_Rehersal), se_AMQrehersal= (sd(AMQ_Rehersal)/ (n() -1) ),
          mean_AMQintensity= mean(AMQ_Intensity),se_AMQintensity = (sd(AMQ_Intensity)/ (n() -1)))



means_data_long_rehearsed <- pivot_longer(means_data_rehearsed, -memory_type, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide_rehearsed <- pivot_wider(means_data_long_rehearsed, names_from = measure, values_from = value)
means_data_wide_rehearsed$condition <- "rehearsed"



means_data_nonreh <- data %>% 
  filter(rehearsed_condition== 0) %>%
group_by(memory_type) %>% 

  summarize(mean_AMQsee= mean(AMQ_see), se_AMQsee= (sd(AMQ_see)/ (n() -1)), 
          mean_AMQhear= mean(AMQ_hear), se_AMQhear= (sd(AMQ_hear)/ (n() -1) ),
             mean_AMQlive= mean(AMQ_Live), se_AMQlive= (sd(AMQ_Live)/ (n() -1) ),
          mean_AMQstrength= mean(AMQ_Strength), se_AMQstrength= (sd(AMQ_Strength)/ (n() -1) ),
          mean_AMQpositivity= mean(AMQ_Positivity), se_AMQpositivity= (sd(AMQ_Positivity)/ (n() -1) ),
          mean_AMQnegativity= mean(AMQ_Negativity), se_AMQnegativity= (sd(AMQ_Negativity)/ (n() -1) ),
          mean_AMQaccuracy= mean(AMQ_Accuracy), se_AMQaccuracy= (sd(AMQ_Accuracy)/ (n() -1) ),
          mean_AMQrehersal= mean(AMQ_Rehersal), se_AMQrehersal= (sd(AMQ_Rehersal)/ (n() -1) ),
          mean_AMQintensity= mean(AMQ_Intensity),se_AMQintensity = (sd(AMQ_Intensity)/ (n() -1)))



means_data_long_nonreh <- pivot_longer(means_data_nonreh, -memory_type, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide_nonreh <- pivot_wider(means_data_long_nonreh, names_from = measure, values_from = value)
means_data_wide_nonreh$condition <- "non-rehearsed"

means_data_wide_all <- bind_rows(means_data_wide_rehearsed, means_data_wide_nonreh)


library(ggthemes)

ggplot(means_data_wide_all, aes(x=mean, y= variable, color= memory_type)) +
  facet_grid(~condition) + 
  geom_point(size= 3.5) +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se),  width= 0.5, size= 1) +
  coord_cartesian(xlim=c(1,7)) +
  theme_classic()





```



```{r ttest graph AMQ}

data_ttest_1 <- data %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_ttest_2 <- data %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_ttest <- bind_rows(data_ttest_1, data_ttest_2)  
data_ttest$condition <- paste(data_ttest$memory_type, data_ttest$rehearsed_condition, sep="_")

data_ttest



#develop graph

means_data <- data_ttest %>% 
group_by(condition) %>% 

  summarize(mean_AMQsee= mean(AMQ_see), se_AMQsee= (sd(AMQ_see)/ (n() -1)), 
          mean_AMQhear= mean(AMQ_hear), se_AMQhear= (sd(AMQ_hear)/ (n() -1) ),
             mean_AMQlive= mean(AMQ_Live), se_AMQlive= (sd(AMQ_Live)/ (n() -1) ),
          mean_AMQstrength= mean(AMQ_Strength), se_AMQstrength= (sd(AMQ_Strength)/ (n() -1) ),
          mean_AMQpositivity= mean(AMQ_Positivity), se_AMQpositivity= (sd(AMQ_Positivity)/ (n() -1) ),
          mean_AMQnegativity= mean(AMQ_Negativity), se_AMQnegativity= (sd(AMQ_Negativity)/ (n() -1) ),
          mean_AMQaccuracy= mean(AMQ_Accuracy), se_AMQaccuracy= (sd(AMQ_Accuracy)/ (n() -1) ),
          mean_AMQrehersal= mean(AMQ_Rehersal), se_AMQrehersal= (sd(AMQ_Rehersal)/ (n() -1) ),
          mean_AMQintensity= mean(AMQ_Intensity),se_AMQintensity = (sd(AMQ_Intensity)/ (n() -1)))



means_data_long <- pivot_longer(means_data, -condition, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide <- pivot_wider(means_data_long, names_from = measure, values_from = value)


library(ggthemes)

ggplot(means_data_wide, aes(x=mean, y= variable, color= condition)) +
  geom_point(size= 3.5) +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se),  width= 0.5, size= 1) +
  coord_cartesian(xlim=c(1,7)) +
  theme_classic()



```



```{r tale-facet-grid-descriptives-graph}



data_TALE <- data %>% 
    mutate(directive_TALE= (TALE_1 + TALE_6)/2) %>% 
    mutate(self_TALE= (TALE_2 + TALE_4)/2) %>% 
    mutate(social_TALE= (TALE_5))



means_data_rehearsed <- data_TALE %>% 
  filter(rehearsed_condition== 1)  %>% 
group_by(memory_type) %>% 

  summarize(mean_directive= mean(directive_TALE), se_directive= (sd(directive_TALE)/ (n() -1)), 
          mean_self= mean(self_TALE), se_self= (sd(self_TALE)/ (n() -1) ),
             mean_social= mean(social_TALE), se_social= (sd(social_TALE)/ (n() -1) ))


means_data_long_rehearsed <- pivot_longer(means_data_rehearsed, -memory_type, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide_rehearsed <- pivot_wider(means_data_long_rehearsed, names_from = measure, values_from = value)
means_data_wide_rehearsed$condition <- "rehearsed"



means_data_nonreh <- data_TALE %>% 
  filter(rehearsed_condition== 0) %>%
group_by(memory_type) %>% 
 summarize(mean_directive= mean(directive_TALE), se_directive= (sd(directive_TALE)/ (n() -1)), 
          mean_self= mean(self_TALE), se_self= (sd(self_TALE)/ (n() -1) ),
             mean_social= mean(social_TALE), se_social= (sd(social_TALE)/ (n() -1) ))


means_data_long_nonreh <- pivot_longer(means_data_nonreh, -memory_type, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide_nonreh <- pivot_wider(means_data_long_nonreh, names_from = measure, values_from = value)
means_data_wide_nonreh$condition <- "non-rehearsed"

means_data_wide_all <- bind_rows(means_data_wide_rehearsed, means_data_wide_nonreh)


library(ggthemes)

ggplot(means_data_wide_all, aes(x=mean, y= variable, color= memory_type)) +
  facet_grid(~condition) + 
  geom_point(size= 3.5) +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se),  width= 0.5, size= 1) +
  coord_cartesian(xlim=c(1,7)) +
  theme_classic()





```


```{r TALE-ttest- graph}

data_ttest_1_tale <- data_TALE %>% 
  filter(rehearsed_condition==0 & memory_type=="personal") 
data_ttest_2_tale <- data_TALE %>%
  filter(rehearsed_condition==1 & memory_type=="fiction")
data_ttest <- bind_rows(data_ttest_1_tale, data_ttest_2_tale)  
data_ttest$condition <- paste(data_ttest$memory_type, data_ttest$rehearsed_condition, sep="_")

data_ttest



#develop graph

means_data <- data_ttest %>% 
group_by(condition) %>% 

    summarize(mean_directive= mean(directive_TALE), se_directive= (sd(directive_TALE)/ (n() -1)), 
          mean_self= mean(self_TALE), se_self= (sd(self_TALE)/ (n() -1) ),
             mean_social= mean(social_TALE), se_social= (sd(social_TALE)/ (n() -1) ))


means_data_long <- pivot_longer(means_data, -condition, names_to= c("measure", 'variable'), names_sep= "_", values_to = "value") 

means_data_wide <- pivot_wider(means_data_long, names_from = measure, values_from = value)


library(ggthemes)

ggplot(means_data_wide, aes(x=mean, y= variable, color= condition)) +
  geom_point(size= 3.5) +
  geom_errorbar(aes(xmax=mean + se , xmin= mean- se),  width= 0.5, size= 1) +
  coord_cartesian(xlim=c(1,7)) +
  theme_classic()



```

The only different one is social (higher for rehearsed fictional memories)
Directive and self are not significantly different

